Enabling Ambient Backscatter \\Using Low-Cost Software Defined Radio

### 2017-04-07 paper.tex
Cleanup the abstract a little

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
Backscatter communication is attractive for energy-constrained devices due to its very low power requirements. Ambient backscatter takes this aspect to the limit by leveraging existing radio frequency signals for the purpose of communication without the need for generating energy expensive carrier signal. In this paper we investigate the use of ambient television broadcast signals for communication. As opposed to state-of-the-art restricted to operations under conditions of strong signal strength, we demonstrate a low cost software defined radio as receiver 
enables operations even in conditions when ambient signals are  weak in strength. We build the system using low-cost off-the-shelf microcontroller, and RTLSDR software-defined radio receiver. We also conduct survey of signal strength of TV broadcast in a mid-sized swedish city, and observe that our system can operate in most parts of the city.
\end{abstract}

>>>>

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
Backscatter communication is attractive for energy-constrained devices
				due to its very low power requirements. Ambient backscatter
				takes this point to the limit by leveraging existing radio
				frequency signals for the purpose of communication, without the
				need for generating an energy-expensive carrier signal. In this
				paper we investigate the use of television broadcast signals as
				a carrier for backscatter communication. As opposed to the
				state-of-the-art, restricted to operations under conditions of
				high signal strength, we demonstrate a low-cost software defined
				radio receiver that operates even in conditions when ambient
				signals are weak. We build the system using a low-cost
				off-the-shelf microcontroller and an RTLSDR software-defined
				radio receiver. We also conduct a survey of the signal strength
				of TV broadcast in a mid-sized Swedish city and observe that our
				system can operate in most parts of the city.
\end{abstract}
